SMASH companion source code repository

### 2021-06-02 analysis/index.Rmd
wflow_publish("analysis/index.Rmd")
workflowr::wflow_publish("index.Rmd")

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2019).
> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
> [arXiv:1605.07787][smash-preprint].

@@

The following analyses generate some of the empirical results
presented in [Xing, Carbonetto & Stephens (2019)][smash-preprint]. If
you encounter a problem running any of the R code in these examples,
please post an [issue][issues].

@@

Copyright (c) 2016-2019, Zhengrong Xing, Peter Carbonetto & Matthew
Stephens.

>>>>

> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2020).
> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
> [arXiv:1605.07787][smash-preprint].

@@

The following analyses generate some of the empirical results
presented in [Xing, Carbonetto & Stephens (2020)][smash-preprint]. If
you encounter a problem running any of the R code in these examples,
please post an [issue][issues].

@@

Copyright (c) 2016-2021, Zhengrong Xing, Peter Carbonetto & Matthew
Stephens.
